Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-14 analysis/paper/paper.Rmd
Reorder and create section on limitations to approach taken
Edits for clarity

The methods for selecting articles meant that only page numbers between 1 and 150 were selected.
This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, e.g., *Phytopathology*® have focus issues with invited authors.
In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct and more importantly, may show that even when authors are specifically recruited that they are no more likely to share the supporting materials for the articles that they write.

@@

@@

Plant pathology is not alone in the lack of reproducibility and with the close-nature of data and code.
In response to this, other related disciplines have published guides or started communities to promote and support tools and methods that promote good practices that lead to open and reproducible research.In entomology @Wittman2020 published "A Guide and Toolbox to Replicability and Open Science in Entomology", which documented both the benefits and drawbacks of an open and reproducible workflow.
Weed scientists started a community to promote openness in the discipline, Open Weed Science, which stated that they valued, "open access knowledge-sharing as a strategy to enhance reproducibility within our discipline", but the website is no longer available and the Twitter account, \@OpenWeedSci, appears to be inactive when viewing the account as of October 2022 [@OpenWeedScience2021].
@SerradaCruz2019 proposed a framework for capturing provenance of data-centric agronomic experiments using an R-based workflow, 'RFlow', which would allow reuse of R scripts using generic workflows and saving data and metadata to web repositories that other researchers and referees can browse using Web interfaces.
@Kool2020 evaluated the reproducibility of on-farm experiments in Africa, finding that often the experimental design was difficult or impossible to reproduce from the publication.
More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish FAIR data in agriculture [@Smith2018; @Arnaud2020; @Stacey2022].
However, we were unable to find any quantification of the reproducibility of any of these related disciplines as we have done here.

>>>>

@@

## Limitations to Our Approach

Furthermore, the methods for selecting articles meant that only page numbers between 1 and 150 were selected.
This approach assumed that there was no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year and some journals, e.g., *Phytopathology*® have focus issues with invited authors.
In spite of some publications being from special issues, there were no detectable differences in the reproducibility of the articles as defined and measured by this article, so the assumption appears to be correct and more importantly, may show that even when authors are specifically recruited that they are no more likely to share the supporting materials for the articles that they write.

@@

Plant pathology is not alone in the lack of reproducibility and the closed-nature of data and code.
In response to this, other related disciplines have published guides or started communities to promote and support tools and methods that promote good practices that lead to open and reproducible research.In entomology @Wittman2020 published "A Guide and Toolbox to Replicability and Open Science in Entomology", which documented both the benefits and drawbacks of an open and reproducible workflow.
Weed scientists started a community to promote openness in the discipline, Open Weed Science, which stated that they valued, "open access knowledge-sharing as a strategy to enhance reproducibility within our discipline", but the website is no longer available and the Twitter account, \@OpenWeedSci, appears to be inactive when viewing the account as of October 2022 [@OpenWeedScience2021].
@SerradaCruz2019 proposed a framework for capturing provenance of data-centric agronomic experiments using an R-based workflow, 'RFlow', which would allow reuse of R scripts using generic workflows and saving data and metadata to web repositories that other researchers and referees can browse using Web interfaces.
@Kool2020 evaluated the reproducibility of on-farm experiments in Africa, finding that often the experimental design was difficult or impossible to reproduce from the publication.
More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish FAIR data in agriculture [@Smith2018; @Arnaud2020; @Stacey2022].
However, we were unable to find any quantification of the reproducibility of any of these related disciplines as we have done here.
